LCA in R using tidySEM

### 2022-09-04 example_analysis/Daniel_LCA.Rmd
Update Daniel_LCA.Rmd
Added descriptives and one-class solution

@@

```{r}
print("BIC")
print(c("2 class", table_2_class$BIC)) #lowest
print(c("3 class", table_3_class$BIC))
print(c("4 class", table_4_class$BIC))

print("AIC")
print(c("2 class", table_2_class$AIC))
print(c("3 class", table_3_class$AIC))
print(c("4 class", table_4_class$AIC)) #lowest

print("Entropy")
print(c("2 class", table_2_class$Entropy))
print(c("3 class", table_3_class$Entropy)) #highest
print(c("4 class", table_4_class$Entropy))
```
Using the Bootstrapped Likelihood Ratio Test to compare models

```{r}
tidySEM::BLRT(res_2_class)
```

>>>>

# Exploring the data

```{r}
tidySEM::descriptives(df)
```

# 1 class solution

```{r}
# fitting the model
set.seed(123)
mx_lca(data = df, classes = 1) -> res_1_class
```

```{r}
# printing model fit table
print(table_1_class <- tidySEM::table_fit(res_1_class))
```

```{r}
# obtain latent class probabilities
LC_Probabilities_1_class <- tidySEM::class_prob(res_1_class)
print(LC_Probabilities_1_class[1:4])
```
```{r}
# conditional item probabilities
tidySEM::table_prob(res_1_class)
```

@@

```{r}
print("BIC")
print(c("1 class", table_1_class$BIC))
print(c("2 class", table_2_class$BIC)) #lowest
print(c("3 class", table_3_class$BIC))
print(c("4 class", table_4_class$BIC))
```
```{r}
print("AIC")
print(c("1 class", table_1_class$AIC))
print(c("2 class", table_2_class$AIC))
print(c("3 class", table_3_class$AIC))
print(c("4 class", table_4_class$AIC)) #lowest
```

```{r}
print("Entropy")
print(c("1 class", table_1_class$Entropy)) # entropy = 1 
print(c("2 class", table_2_class$Entropy))
print(c("3 class", table_3_class$Entropy)) # highest
print(c("4 class", table_4_class$Entropy))
```

Using the Bootstrapped Likelihood Ratio Test to compare models

```{r}
tidySEM::BLRT()
```
